Gaussian Processes Autoregressive Models for Forecasting the Disturbance Storm Time Index

### 2016-05-24 swsc.tex
Updates from ShareLaTeX

   \author{M. Chandorkar
          \inst{1}
          \and
          E. Camporeale\inst{1}
          }

@@

Model selection of \emph{GP-AR} and \emph{GP-ARX} is performed by grid search methodology and the root mean square error (\emph{RMSE}) on the validation set is used to select the values of the model hyper-parameters. The time lags chosen for \emph{GP-AR} are $p = 6$ while for \emph{GP-ARX} $p=6$, $p_{ex} = 1$ are arrived by experimenting with values starting from one and choosing the value of $p$ yielding best performance on the 63 events in the bench mark.

>>>>

   \author{M. Chandorkar
          \inst{1}
          \and
          S. Wing \inst{1}
          \and
          E. Camporeale\inst{1}
          }

@@

Model selection of \emph{GP-AR} and \emph{GP-ARX} is performed by grid search methodology and the root mean square error (\emph{RMSE}) on the validation set is used to select the values of the model hyper-parameters. Figure \ref{fig:energy} shows a contour plot of the \emph{RMSE} computed on the validation data for the \emph{GP-ARX} model, the x axis represents the intercept $b$ of the polynomial kernel while the y axis represents $\sigma$ the standard deviation of the noise of the GP model as seen in section \ref{sec:inference}. In the experiments performed the best performing values of the hyper-parameters outputted by the grid search routing are $b = 0.002,\ \sigma = 1.994$.

The time lags chosen for \emph{GP-AR} are $p = 6$ while for \emph{GP-ARX} $p=6$, $p_{ex} = 1$ are arrived by experimenting with values starting from one and choosing the value of $p$ yielding best performance on the 63 events in the bench mark.
